A simulation-based assessment of the relation between Stone Age sites and relative sea-level change along the Norwegian Skagerrak coast

### 2022-02-04 analysis/paper/paper.Rmd
Re-dating previously shoreline dated sites

@@

When no other information is available it can be recommended to apply the method for shoreline dating outlined above, which involves both taking the distance between sites and the isobase of displacement curves into consideration, and implementing to account for the distance between the sites and the shoreline. The precision of this method is, as shown above, both geographically and temporally contingent where older sites towards the north-east will get a more precise date than younger sites located towards the south-west. This approach will be useful either when shoreline dating a large number of sites where no other information is available [e.g. @solheim2018; @fossum2020; @nielsen2021b; @breivik2014], which is typically done using a uniform range of uncertainty, likely overestimating the precision of the method in most cases and possibly underestimating it in some.

>>>>

# Shoreline dating

```{r redate, echo = FALSE, fig.cap = "Shoreline dating sites from the study area without radiocarbon dates or with radiocarbon dates that do not corresponding to the site inventories. These are comapred to the shoreline dates originally proposed by the excavation reports in black.", out.width = "525px", fig.align="center", regfloat=TRUE}
knitr::include_graphics(here("analysis/figures/redate.png"))
```

@@

When no other information is available it can be recommended to apply the method for shoreline dating outlined above, which involves both taking the distance between sites and the isobase of displacement curves into consideration, and implementing to account for the distance between the sites and the shoreline. The precision of this method is, as shown above, both geographically and temporally contingent, where older sites situated towards the north-east will get a more precise date than younger sites located towards the south-west. This approach will be useful either when shoreline dating a large number of sites where no other information is available [e.g. @solheim2018; @fossum2020; @nielsen2021b; @breivik2014], which is typically done using a uniform range of uncertainty, likely overestimating the precision of the method in most cases and possibly underestimating it in some.

The outlined approach is thus derived from the available radiocarbon record, and appears to be able to accommodate the available data. To further test the method will require independently derived radiocarbon dates.
